Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-09-02 reviews.Rmd

We respectfully disagree.
What makes the arguments "Bayesian" is our interpretation of probabilities.
For a Bayesian, they represent degrees of belief.
For a frequentist, they represent (relative) frequencies of events that result from a random process.
This is a subtle but most important distinction.

@@

Yes, the Bayes formula can be conceptualized as a likelihood ratio scaled by priors.
However, the mere use of the likelihood ratio in the Bayes theorem can not be grounds to reduce Bayesianism to likelihood ratios.

@@

Let us cite <https://doi.org/10.3758/s13423-022-02069-1"Nowhere in Mayo’s severity principle or in the specifications discussed below is the riskiness or specificity of a hypothesis, and the predictions it makes, incorporated as a requirement for a severe test (Meehl, 1978; 1986; 1990b, a; Roberts & Pashler, 2000)."

@@

Our claim is that uncertainty is reduced, not theoretical risk directly.
We claim that there are exploratory methods with a well-known error rate.
For example, a neural network has extreme flexibility in fitting the data closely, yet it is calculable.

@@

Somehow, our argument seems to be flipped here.
An exploratory study has low theoretical risk.
A preregistered study has low uncertainty about theoretical risk.
A preregistered exploratory study is more persuasive than a study with the same exploration going on that is not preregistered.

@@

Yes, indeed, this could all have low theoretical risk.
We could include the disclaimer to the examples on p. 13 "Note that the three tests differ in theoretical risk even when they are tested with the same Type 1 error rate."

@@

We have discussed Mayo's Severity to show that these approaches fundamentally differ, and we have significantly extended the discussion to include literature that also uses a Bayesian rationale to investigate what methods researchers should employ.
Additionally, we substantiated the "strawman" further because we believe that the minimizing vs communicating researchers' degrees of freedom confusion is at the centre of many debates around preregistration.

>>>>

We respectfully disagree.
What makes the arguments "Bayesian" is our interpretation of probabilities.
For a Bayesian, they represent degrees of belief.
For a frequentist, they represent (relative) frequencies of events that result from a random process.
This is a subtle but most important distinction.
A Bayesian may assign a probability to a hypothetical world where a paper was p hacked, since probabilities represent their subjective believes.
A frequentist (and hence severe tester), can not possibly assign a probability here because there is no random process but a single event that happened in the past, so the paper was either p hacked or not.
This is similar to the mistake, in frequentist philosophy, to say that an effect is with 95% probability in the confidence interval.

@@

However, the mere use of the likelihood ratio in the Bayes theorem can not be grounds to reduce Bayesianism to likelihood ratios.

@@

Let us cite <https://doi.org/10.3758/s13423-022-02069-1> "Nowhere in Mayo’s severity principle or in the specifications discussed below is the riskiness or specificity of a hypothesis, and the predictions it makes, incorporated as a requirement for a severe test (Meehl, 1978; 1986; 1990b, a; Roberts & Pashler, 2000)."

@@

Our claim is that uncertainty is reduced, not theoretical risk directly.
We claim that there are exploratory methods with a well-known error rate.
In our argument, the difference between a t-test and a random forest is a matter of degree and not of kind.
A t-test may maintain its 5%-alpha error and a random forest may find a variable important 30% of the time.
For both, however, their behavior is mathematically analyzable, yielding a concrete expectation for their theoretical risk.

@@

Somehow, our argument seems to be flipped here.
An exploratory study has low theoretical risk.
A preregistered study has low uncertainty about theoretical risk.
A preregistered exploratory study is more persuasive than a study with the same degree of exploration that is not preregistered.

@@

Yes, indeed, these could all have low theoretical risk.
We could include the disclaimer to the examples on p. 13 "Note that the three tests differ in theoretical risk even when they are tested with the same Type 1 error rate."

@@

We have discussed Mayo's Severity to show that these approaches fundamentally differ, and we have significantly extended the discussion to include literature that also uses a Bayesian rationale to investigate what methods researchers should employ.
Additionally, we substantiated the "strawman" further because we believe that the minimizing vs communicating researchers' degrees of freedom confusion is at the center of many debates around preregistration.
